Multimodal Corpora

### 2017-01-16 paper.tex
Add introduction

  	\section{Introduction}
		\Todo{Add definitions and intro to multimodal corpora}

@@

		\subsection{Recording Scenario}
			As the goal was to record speech in combination with gestures, the recording scenario had to chosen such that a sufficient amount of gestures was produced by the speaker. Furthermore the gestures should be easily interpretable to aid the annotation process and not externally forced to prevent unnatural ones. Therefore a scenario with the following properties was chosen \cite[ch. 2]{Bielefeld2010}:	
			\begin{itemize}
				\item The topic of the recorded converations was a spatial communication task. The participant had to give directions and describe landmarks. The descision for this topic was based on the evidence for a higher use of gestures, when speaking about spatial topics, provided by \cite[p. 313]{Alibali2005}. This ensured the appropriate amount of easily interpretable gestures.
				\item The stimulus for the participants was a "bus tour" through a virtual city. This was presented in \gls{vr} to make sure ensure the exact same stimulus for each participant. This improved the comparibility of the individual participant data.
				\item After receiving the stimulus, the participant had to describe the "bus tour" and the included landmarks to another person, who has not seen the stimulus. This provided a natural yet controlled conversation scenario for the participant.
			\end{itemize}

>>>>

  	\section{Introduction}
		Datasets such as corpora are an important part in training and evaluation of an intelligent systems. A corpus is a structured collection of data of one or multiple modalities. Those modalities are for example written text, audio or video recordings of an experiment. Corpora which incorporate multiple modalities are called multimodal corpora. This paper will give a short overview over three of them. The first one being the BAS SmartKom Corpus with the focus set on human computer interaction. The second corpus is the Callas Expressivity Corpus where cross-cultural differences in gestures is the motivation for the creation. The last corpus, which is the Bielefeld Speech and Gesture Alignment Corpus, is about speech and gestures in a face to face conversation.

@@

		\subsection{Recording Scenario}
			As the goal was to record speech in combination with gestures, the recording scenario had to be chosen such that a sufficient amount of gestures was produced by the speaker. Furthermore the gestures should be easily interpretable to aid the annotation process and not externally forced to prevent unnatural ones. Therefore a scenario with the following properties was chosen \cite[ch. 2]{Bielefeld2010}:	
			\begin{itemize}
				\item The topic of the recorded converations was a spatial communication task. The participant had to give directions and describe landmarks. The descision for this topic was based on the evidence for a higher use of gestures, when speaking about spatial topics, provided by \cite[p. 313]{Alibali2005}. This ensured the appropriate amount of easily interpretable gestures.
				\item The stimulus for the participants was a "bus tour" through a virtual city. This was presented in \gls{vr} to make sure ensure the exact same stimulus for each participant. This improved the comparibility of the individual participant data.
				\item After receiving the stimulus, the participant had to describe the "bus tour" and the included landmarks to another person, who has not seen the stimulus. This provided a natural yet controlled conversation scenario for the participant.
			\end{itemize}
